Estimating individual subjective values of emotion regulation strategies

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Subjective values of emotion regulation strategies}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 5627}
\usepackage{lineno}

@@

The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning.\textsuperscript{2}
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification,\textsuperscript{1} and, following the taxonomy of Powers and LaBar,\textsuperscript{3} individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process.\textsuperscript{1}
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy.\textsuperscript{1}
This postulated temporal sequence of ER strategies influences their effectiveness.
Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}

Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see Zaehringer et al.\textsuperscript{5}).
Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with \emph{d\textsubscript{-}} = 0.32.\textsuperscript{5}
In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal.\textsuperscript{6}
Similar effects have been reported for suppression,\textsuperscript{6} distancing,\textsuperscript{7} and distraction.\textsuperscript{8}
Importantly, results on electromyographic measures seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.

Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences.
In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being.\textsuperscript{9}
In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.\textsuperscript{10}), which led to the postulation of \emph{adaptive} (such as reappraisal, acceptance) and \emph{maladaptive} (such as suppression, rumination) ER strategies.
For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms.\textsuperscript{11}

The postulation of \emph{adaptive} and \emph{maladaptive} ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
Within this framework, \emph{maladaptive} refers to inflexible ER strategy use or use of strategies that are hindering goal achievement.\textsuperscript{12}
Adaptive flexible ER requires a large repertoire of ER strategies.\textsuperscript{12}
The term ``repertoire'' can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities.\textsuperscript{13}
A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology.\textsuperscript{14--16}
Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{17}

How do people choose strategies from their repertoire?
Similarly to the expectancy-value model of emotion regulation\textsuperscript{18} it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice\textsuperscript{19}) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs\textsuperscript{20}.
For example, a study found that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{21}
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction.\textsuperscript{20,21}
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{20,22}
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy.\textsuperscript{22}
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
Furthermore, the research on ER choice lacks information regarding the strategies that were \emph{not} chosen in each case.
It is unclear whether people had clear preferences or whether the choice options were similarly attractive.

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{12}
One certainly central goal is the regulation of negative affect.
A second, intrinsic and less obvious goal is the avoidance of effort.\textsuperscript{23}
When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{24}
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibility, however, would show high SVs only for one or very few strategies.
This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from.
Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.

So far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
However, this would be useful to describe interindividual differences in the preference of ER strategies and the ER repertoire more comprehensively.
To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED).\textsuperscript{25}

In the original study by Westbrook et al.,\textsuperscript{25} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{22}
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{25} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{26}
The paradigm was written and presented using \emph{PsychoPy}.\textsuperscript{27}
We used \emph{R} with \emph{R Studio}\textsuperscript{28,29} with the main packages \emph{afex}\textsuperscript{30} and \emph{BayesFactor}\textsuperscript{31} for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

The newly developed ER paradigm was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
In accordance with our previous study,\textsuperscript{22} we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}

@@

Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{32} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
The second session will comprise the ER paradigm and take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{33,34}

@@

The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale.\textsuperscript{35,36}
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{39} will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{9,40}
For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{41}
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from.\textsuperscript{42}
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{43,44} will be used.
To assess self-control,\textsuperscript{45} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS),\textsuperscript{46} the Brief Self-Control Scale (BSCS),\textsuperscript{47,48} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{49,50}
Attentional control will be assessed using the Attentional Control Scale (ACS).\textsuperscript{51}
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group.\textsuperscript{22}
Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition ``active viewing-neutral'' that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to ``actively view all pictures and permit all emotions that may arise.''
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to ``suppress their emotional facial expression.''
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{22}
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
It was followed by neutral or negative picture for a total of 6 seconds.
After each block, participants retrospectively rated their subjective emotional arousal on a continous scale (ranging from ``not at all aroused'' to ``very highly aroused'') and their subjective effort (ranging from ``not very exhausting'' to ``very exhausting'') using a slider on screen.

\emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{25} with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), two strategies with monetary values will be presented.
The order of the comparisons will be randomized.
Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option ``1 € for strategy A or 1 € for strategy B''.
The strategy that is not chosen will be assigned the value of 2 €.
From this point on, comparisons between strategies will follow the original COG-ED paradigm.\textsuperscript{25}
Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.

@@

Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{52} and the International Affective Picture System (IAPS).\textsuperscript{53}
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
An evolutionary algorithm\textsuperscript{54} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material 1.

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Subjective values of emotion regulation strategies}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 5630}
\usepackage{lineno}

@@

The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning\textsuperscript{2}.
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification\textsuperscript{1}, and, following the taxonomy of Powers and LaBar\textsuperscript{3}, individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process\textsuperscript{1}.
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy\textsuperscript{1}.
This postulated temporal sequence of ER strategies influences their effectiveness.
Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45\textsuperscript{4}.

Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see Zaehringer et al.\textsuperscript{5}).
Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with \emph{d\textsubscript{-}} = 0.32\textsuperscript{5}.
In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal\textsuperscript{6}.
Similar effects have been reported for suppression\textsuperscript{6}, distancing\textsuperscript{7}, and distraction\textsuperscript{8}.
Importantly, results on electromyographic measures seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.

Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences.
In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being\textsuperscript{9}.
In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.\textsuperscript{10}), which led to the postulation of \emph{adaptive} (such as reappraisal, acceptance) and \emph{maladaptive} (such as suppression, rumination) ER strategies.
For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms\textsuperscript{11}.

The postulation of \emph{adaptive} and \emph{maladaptive} ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
Within this framework, \emph{maladaptive} refers to inflexible ER strategy use or use of strategies that are hindering goal achievement\textsuperscript{12}.
Adaptive flexible ER requires a large repertoire of ER strategies\textsuperscript{12}.
The term ``repertoire'' can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities\textsuperscript{13}.
A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology\textsuperscript{14--16}.
Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life\textsuperscript{17}.

How do people choose strategies from their repertoire?
Similarly to the expectancy-value model of emotion regulation\textsuperscript{18} it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice\textsuperscript{19}) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs\textsuperscript{20}.
For example, a study found that the intensity of a stimulus or situation plays a role in the choice\textsuperscript{21}.
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction\textsuperscript{20,21}.
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort\textsuperscript{20,22}.
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy\textsuperscript{22}.
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
Furthermore, the research on ER choice lacks information regarding the strategies that were \emph{not} chosen in each case.
It is unclear whether people had clear preferences or whether the choice options were similarly attractive.

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement\textsuperscript{12}.
One certainly central goal is the regulation of negative affect.
A second, intrinsic and less obvious goal is the avoidance of effort\textsuperscript{23}.
When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24}.
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibility, however, would show high SVs only for one or very few strategies.
This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from.
Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.

So far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
However, this would be useful to describe interindividual differences in the preference of ER strategies and the ER repertoire more comprehensively.
To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED)\textsuperscript{25}.

In the original study by Westbrook et al.\textsuperscript{25}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies\textsuperscript{22}.
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{25} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{26}).

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{27}.
The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{28}.
We used \emph{R} with \emph{R Studio}\textsuperscript{29,30} with the main packages \emph{afex}\textsuperscript{31} and \emph{BayesFactor}\textsuperscript{32} for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

The newly developed ER paradigm was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
In accordance with our previous study\textsuperscript{22}, we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}

@@

Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{33} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
The second session will comprise the ER paradigm and take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{34,35}.

@@

The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{36,37}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{40} will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,41}.
For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{42}.
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{43}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{44,45} will be used.
To assess self-control,\textsuperscript{46} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{47}, the Brief Self-Control Scale (BSCS)\textsuperscript{48,49}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{50,51}.
Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{52}.
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group\textsuperscript{22}.
Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition ``active viewing-neutral'' that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to ``actively view all pictures and permit all emotions that may arise.''
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to ``suppress their emotional facial expression.''
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite\textsuperscript{22}.
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
It was followed by neutral or negative picture for a total of 6 seconds.
After each block, participants retrospectively rated their subjective emotional arousal on a continous scale (ranging from ``not at all aroused'' to ``very highly aroused'') and their subjective effort (ranging from ``not very exhausting'' to ``very exhausting'') using a slider on screen.

\emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{25} with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), two strategies with monetary values will be presented.
The order of the comparisons will be randomized.
Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option ``1 € for strategy A or 1 € for strategy B''.
The strategy that is not chosen will be assigned the value of 2 €.
From this point on, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{25}.
Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.

@@

Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{53} and the International Affective Picture System (IAPS)\textsuperscript{54}.
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
An evolutionary algorithm\textsuperscript{55} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material 1.
